Analyzing Security-Cost Trade-off for a \\ Fully Homomorphic Encryption Scheme

### 2013-06-17 Report/article.tex
jo

\subsection{Cost of the Cryptosystem}
 In the SV scheme, performing any operation on encrypted bits requires  \texttt{KeyGen}, \texttt{Encrypt}, \texttt{Add},\texttt{ Mult}, \texttt{Recrypt}, \texttt{Decrypt}, and hence we measure their performance in terms of run time. These measurements are done by varying the parameter $N$(keeping all other parameters fixed) that determines the degree of all intermediate polynomials of the cryptosystem. The measurements in this section were taken on M2. From \autoref{common cost}, we can infer that the cost of these functions increase with the increase of the degree of the polynomial $F(x)$. Futhermore, we observe that the size of the public key is increasing linearly with $n$  where $N=2^n$.

@@

\begin{table}[htb]
  \centering
  \caption{Trade-off for 10000 multiplications}
\begin{tabular}{|c|c|c|c||}
  \hline
  \multicolumn{4}{|c||}{$\eta = 2^{300}$ , $N=8$} \\
  \hline
  $\mu$ &  time(in s)  & depth & $2^{\frac{N}{\epsilon}}$ \\
  \hline
  $2$ & 527  & 6.90 & 1.01887 \\
  $4$ & 526 & 5.89 & 1.01894 \\
  $8$ & 528  & 5.63 & 1.01900 \\
  $16$ & 529  & 5.40 & 1.01907 \\
   \hline
\end{tabular}
\normalsize
\label{tab:tradeofftab2}
\end{table}

>>>>

\subsection{Cost of the Cryptosystem}
 In the SV scheme, performing any operation on encrypted bits requires  \texttt{KeyGen}, \texttt{Encrypt}, \texttt{Add},\texttt{ Mult}, \texttt{Recrypt}, \texttt{Decrypt}, and hence we measure their performance in terms of run time. These measurements are done by varying the parameter $N$(keeping all other parameters fixed) that determines the degree of all intermediate polynomials of the cryptosystem. The measurements in this section were taken on M2. From \autoref{common cost}, we can infer that the cost of these functions increase with the increase of the degree of the polynomial $F(x)$. Futhermore, we observe that the size of the public key is increasing with the increase of $N$ which can be explained by the fact that the resultant of 2 polynomials increases with the increase of the degree which makes the prime number $p$ harder to be found and so it increases the duration of key generation.

@@

\begin{table}[htb]
  \centering
  \caption{Trade-off for 10000 multiplications}
\begin{tabular}{|c|c|c|c||}
  \hline
  \multicolumn{4}{|c||}{$\eta = 2^{300}$ , $N=8$} \\
  \hline
  $\mu$ &  time(in s)  & depth & $2^{\frac{N}{\epsilon}}$ \\
  \hline
  $2$ & 527  & 6.90 & 1.01887 \\
  $4$ & 526 & 5.89 & 1.01894 \\
  $8$ & 528  & 5.63 & 1.01900 \\
  $16$ & 529  & 5.40 & 1.01907 \\
  $32$ & 801  & 5.40 & 1.01907 \\
  $64$ & 824  & 5.40 & 1.01907 \\

   \hline
\end{tabular}
\normalsize
\label{tab:tradeofftab2}
\end{table}
